---
title: "Wisconsin Income Plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

## Authors

**TODO**: Write Down Authors' Full Name and Email Address


## Introduction

**TODO**: Write down brief explanation what we are trying to plot, why it is useful, reason why we are narrowing down to the Wisconsin's Data. Include our topic.


## Data

```{r loadData}

library(tidyverse) ## To clean up data much easier

# Read CSV data
All_Income <- read.csv("2017_All_County_QCEW_AnnualAverage_Total.csv")
head(All_Income)

```

**TODO**: What does this data for? How it looks like? Include the meaning of each column, we need to seelct some.


## Select Wisconsin's Data

```{r selectWisconsin}

## Retrieve Index of row containing Wisconsin's data
WI_Index <- which(substr(All_Income$area_fips, 1, 2) == "55")
## Filter Wisconsin's Data
WI_Income <- All_Income[WI_Index, ]

## Clean useless data and values
rm(WI_Index, All_Income)

```

First two digit of FIPS code indicates each state
**TODO**: Some description
Reference: https://www.nrcs.usda.gov/wps/portal/nrcs/detail/?cid=nrcs143_013696


## Select Column for Plotting


## Making Plot