---
title: "Wisconsin Income Plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

## Authors

**TODO**: Write Down Authors' Full Name and Email Address


## Introduction

We are trying to analyze the relationship between economic status and education in Wisconsin. To do this, we are focusing on high school data for Wisconsin, and using proxy variables in each county such as average ACT Score, average GPA, and high school graduation rate. For the economic status data, we are analyzing the variables mean income, annual wage per employee, GDP for a county, and tax revenue. Because education is generally left up the states, the education data in the United States is very divided. Because of this, we decided to focus only on Wisconsin to analyze this relationship because it would not be very time efficient to have to combine 50 different data sets into one.  

To begin analyzing the relationship between these two things, we started by making a graph of annual wage per employee for each county in Wisconsin. This can be used gauge which citizens within the counties of the state are making more money compared to others, we are using this as a proxy variable for economic status.  


## Data

```{r loadData}

library(tidyverse) ## To clean up data much easier

# Read CSV data
All_Income <- read.csv("2017_All_County_QCEW_AnnualAverage_Total.csv")
head(All_Income)

```

**TODO**: What does this data for? How it looks like? Include the meaning of each column, we need to seelct some.


## Select Wisconsin's Data

```{r selectWisconsin}

## Retrieve Index of row containing Wisconsin's data
WI_Index <- which(substr(All_Income$area_fips, 1, 2) == "55")
## Filter Wisconsin's Data
WI_Income <- All_Income[WI_Index, ]

## Clean useless data and values
rm(WI_Index, All_Income)

```

First two digit of FIPS code indicates each state
**TODO**: Some description
Reference: https://www.nrcs.usda.gov/wps/portal/nrcs/detail/?cid=nrcs143_013696


## Select Data for Plotting

```{r selectDataForPlotting}

# Filtering Rows in order to see the total incomes of each counties of Wisconsin
WI_Total_Income_Index <- which(WI_Income$own_code == 0)
WI_Total_Income <- WI_Income[WI_Total_Income_Index, ]
# Clearing useless data
rm(WI_Income, WI_Total_Income_Index)

# Remove 2 extra rows in the WI_Total_Income
# Wisconsin has 72 counties, but it contains 74 rows
notCountyFIPS <- which(WI_Total_Income$area_fips == "55000" | ## For WI cummulated
                         WI_Total_Income$area_fips == "55999" ## For WI Unknowns
                       )
WI_Total_Income <- WI_Total_Income[-notCountyFIPS, ]
# Clearing useless data
rm(notCountyFIPS)


# Filter meaningful columns
WI_Total_Income <- as_tibble(
  list(
    countyFIPS = as.numeric(as.character(WI_Total_Income$area_fips)), ## FIPS code to indicate each county
    annualAvgQuarterlyEstablishments = WI_Total_Income$annual_avg_estabs,
    annualAvgEmployments = WI_Total_Income$annual_avg_emplvl,
    totalAnnualWage = WI_Total_Income$total_annual_wages, ## Total wages (Income)
    ## Taxable income and contribution will follow the tendency of total annual wages
    averageWeeklyWage = WI_Total_Income$annual_avg_wkly_wage,
    annualWagesPerEmployee = WI_Total_Income$avg_annual_pay
  )
)



```

**TODO** Write down some description what and why we are doing here.
Reference: https://data.bls.gov/cew/doc/titles/ownership/ownership_titles.htm
Reference: https://en.wikipedia.org/wiki/List_of_counties_in_Wisconsin
Reference: http://www.dlt.ri.gov/lmi/faq/employment.htm


## Making Plot

```{r plot, fig.height = 20, fig.asp = 1, fig.align = "center"}

library(choroplethr)

## Plotting for totalAnnualWage of each county
### Need to make separated dataframe
### region = countyFIPS
### value = totalAnnualWage
df <- as_tibble(
  list(
    region = WI_Total_Income$countyFIPS,
    value = WI_Total_Income$totalAnnualWage
  )
)
county_choropleth(df, state_zoom="wisconsin",
                  title = "2017 Total Annual Wage of counties in the Wisconsin",
                  legend = "Total Annual Wage (USD)",
                  num_colors = 1)

## Plotting for annualAveragePerEmployee of each county
### Need to make separated dataframe
### region = countyFIPS
### value = annualAveragePerEmployee
df <- as_tibble(
  list(
    region = WI_Total_Income$countyFIPS,
    value = WI_Total_Income$annualWagesPerEmployee
  )
)
county_choropleth(df, state_zoom="wisconsin",
                  title = "2017 Annual Wage per Employee of counties in the Wisconsin",
                  legend = "Annual Wages Per Employee (USD)",
                  num_colors = 1)

## clearing useless data
rm(df)

```

**TODO**: Write down some description what we are trying to show


## Discussion Topics/Questions

**TODO**: Make some questions that we might need to get answers from in-class discussion
